XX

### 2019-05-27 paper/manuscript.Rmd
Fix caption map figure

```{r, fig.cap=paste("Graph of", all_int_cites, "data points")}
readd(fig_worldmap)

>>>>

```{r fig-worldmap, fig.width = width('single'), fig.cap = paste("Worldwide distribution of pollination communities included in this study. We compile data from", length(interaction_citations$BIBTEXKEY), "published studies", all_int_cites, "which contain interaction information between plant and their pollinators at", dplyr::n_distinct(int_metadata$loc_id), "distinct locations.")}
readd(fig_worldmap)
